FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2024-07-25 paper.tex
Better description of how injection gets decided

This paper introduces \FlowFPX{}, a toolkit for debugging
\fp{} exceptions~(\cref{s:flowfpx})
that has helped improve a variety of applications,
from ocean simulations to heat modes~(\cref{s:casestudies}).
\FlowFPX{} consists of three tools that can work together to debug \fp{} computations:
\begin{enumerate}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that
    selectively monitors for exceptions and fuzzes Julia code for vulnerabilities.
    \FT{} is a Julia library that operates on Julia code.
  \item
    To visualize results, \FlowFPX{} uses coalesced stack-trace graphs (CSTGs, or
    \CSTG{}s)~\cite{humphreySystematicDebuggingMethods2014}
    to summarize the program contexts that handled exceptional values.
    \CSTG{} is a generic stack-trace graph summarization tool.
  \item
    A companion tool \GPUFPX{}~\cite{llsflg-hpdc-2023} provides fine-grained insights for GPU kernels.
    \GPUFPX{} is a dynamic library that programmers of GPU kernels can use.
\end{enumerate}

@@

\FT{} looks at these parameters in conjunction with stack-trace at the
point where the operation was intercepted to make the decision.
When all the conditions are met, the overloaded operator returns
\Nan{} instead of whatever value would have been computed normally.
This means that \Nan{}s can be injected deep inside of an algorithm,
instead of just at the inputs.
This can reveal vulnerabilities that otherwise would have been
difficult to catch.

@@

When fuzzing reveals an error, the next step is to craft a regression test to
guide repairs.
\FT{} therefore records the sequence of injections that it makes during a fuzzing
run and enables a replay of any recording after the fact.
Replay runs proceed deterministically so that developers can harden
their code and check that the fixes remove the error.
When running a replay, each intercepted operation consults the reply
file (instead of the stack-trace and fuzzing parameters) to decide
whether or not to return a \Nan{} from the computation.

>>>>

This paper introduces \FlowFPX{}, a toolkit for debugging
\fp{} exceptions~(\cref{s:flowfpx})
that has helped improve a variety of applications,
from ocean simulations to heat modes~(\cref{s:casestudies}).
\FlowFPX{} consists of three tools that can work together to debug \fp{} computations:
\begin{enumerate}
  \item
    The centerpiece of \FlowFPX{} is \FT{}, a dynamic analysis tool that
    selectively monitors for exceptions and fuzzes Julia code for vulnerabilities.
    \FT{} is a Julia library that operates on Julia code.
  \item
    To visualize results, \FlowFPX{} uses coalesced stack trace graphs (CSTGs, or
    \CSTG{}s)~\cite{humphreySystematicDebuggingMethods2014}
    to summarize the program contexts that handled exceptional values.
    \CSTG{} is a generic stack trace graph summarization tool.
  \item
    A companion tool \GPUFPX{}~\cite{llsflg-hpdc-2023} provides fine-grained insights for GPU kernels.
    \GPUFPX{} is a dynamic library that programmers of GPU kernels can use.
\end{enumerate}

@@

\FT{} looks at these parameters in conjunction with stack trace at the
point where the operation was intercepted to make the decision.
When fuzzing is active (\texttt{active == true}), there are \Nan{}s
remaining to be injected (\texttt{n\_inject > 0}), and
\texttt{rand(odds)} returns \texttt{1}, then \FT{} inspects the
current stack trace to see if the point is in the dynamic extend of
the wanted \texttt{functions} or \texttt{libraries}.
When all the conditions are met, the overloaded operator returns
\Nan{} instead of whatever value would have been computed normally.
The value \texttt{n\_inject} is decremented before the next operation
gets intercepted.

Since \FT{} checks if it should inject a \Nan{} at \emph{every} \fp{}
operation it intercepts, means that \Nan{}s can be injected deep
inside of an algorithm instead of just at the inputs.
This can reveal vulnerabilities that otherwise would have been
difficult to catch with input-based fuzzers.

@@

When fuzzing reveals an error, the next step is to craft a regression test to
guide repairs.
\FT{} therefore records the sequence of injections that it makes during a fuzzing
run and enables a replay of any recording after the fact.
Replay runs proceed deterministically so that developers can harden
their code and check that the fixes remove the error.
When running a replay, each intercepted operation consults the reply
file (instead of the stack trace and fuzzing parameters) to decide
whether or not to return a \Nan{} from the computation.
